---
title: "Fixed & Random Effects Models for Service Trade"
author: "Saeed, Mohammad Zohaib"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
warning = FALSE
message = FALSE
eval = TRUE
```


```{r}
chooseCRANmirror(graphics = FALSE, ind = 1)
install.packages("marsl")
```

```{r}
library(wooldridge)
library(stargazer)
library(lmtest)
library(plm)
```


```{r}
install.packages("plyr", repos = "http://cran.us.r-project.org")
```


```{r}
library(readxl)
square <- read_excel("C:/Users/zohai/OneDrive/Desktop/square.xlsx", 
    sheet = "this")
View(square)
```



```{r}
library(equatiomatic)
library(zoo)
```



```{r}
library(plm)
pdata.frame(square, index = c("Year", "Country"))
pdim(square)
```


##Fixed Effects Method: Running the model using fixed effects method and plm function

```{r}
library(plm)
library(equatiomatic)
ind1 <- plm(LCO2 ~ STr + GDP + + GDPS + FDI + LCapital + Labor, model = "within", data = square)
library(stargazer)
stargazer(ind1, type = "text", single.row = TRUE, column.labels = c("within"), model.names = FALSE)
```







#Random Effects Model: using Random Effects Model and plm function


```{r}
ind2 <- plm(LCO2 ~ STr + GDP + GDPS + FDI + LCapital + Labor, model = "random", data = square)
stargazer(ind2, type = "text", single.row = TRUE, column.labels = c("Random"), model.names = FALSE)
```


#Hausman Test

phtest(ind1,ind2)

data:  LCO2 ~ STr + GDP + +GDPS + FDI + LCapital + Labor
chisq = 752.36, df = 6, p-value < 2.2e-16
alternative hypothesis: one model is inconsistent

#Conclusion

We will use fixed effects model for service trade as well given the Hausman Test result. 































